\documentclass[10pt,letterpaper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb} 
\usepackage[left=0.25in, right=0.25in, top=0.25in, bottom=0.25in]{geometry}
\title{Constitution OF The Oregon State University Amateur Radio Club (ARC)}
\date{Effective June 21, 2008 \\ Revised Oct 1, 2014}

\begin{document} 
\maketitle


\renewcommand\partname{Article}


\part{Preamble}

We, the undersigned, wishing to secure for ourselves the pleasures and benefits of the association of persons commonly interested in amateur radio, do hereby constitute ourselves the The Oregon State University Amateur Radio Club, and so enact this constitution as our governing law.


\part{Purpose}


It shall be our purpose to facilitate the exchange of information and general cooperation between members, to promote radio knowledge, individual operating efficiency, and to so conduct club programs and activities as to advance the general interest and welfare of amateur radio in the university community.

\part{Description of the Oregon State University Amateur Radio Club (ARC)}

The OSU-ARC is a group of Oregon State University students working collaboratively together in order to facilitate the exchange of information and general cooperation between members, to promote radio knowledge, individual operating efficiency, and to so conduct club programs and activities as to advance the general interest and welfare of amateur radio in the university community.

\part{Members}

\section*{Section 1} Active Members shall be enrolled students at Oregon State University and have attended a group meeting.
\section*{Section 2} Associate members shall be faculty or staff interested in any field related to the goals and projects of the OSU-ARC organization. They shall not be eligible to hold office or vote.
\section*{Section 3} All voting members and officers of OSU-ARC must be students.
\section*{Section 4} Membership shall not be denied to any student on the basis of race, color, national origin, religion, sex, sexual orientation, age, marital status, disability, disabled veteran or Vietnam era veteran status.
\section*{Section 5} Dues may be collected by the club. Dues are set in the by-laws. If there are no dues set in the by-laws then there are no dues.


\part{Officers}

\section*{Section 1} The officers of the association shall be President (P), Vice-President (VP), Secretary, Treasurer, and Station Manager. These officers shall perform the duties prescribed by the constitution and bylaws and by the parliamentary authority adopted by the association. In addition to officers there shall be various group leaders, such that each satellite subgroup has a group leader.
\section*{Section 2} Officers shall be nominated in April or May of each year. Election shall be by secret ballot and the candidates receiving the most votes shall be named to their respective offices.
\section*{Section 3} Officers shall be elected to serve for one year or until their successors are elected, and their terms of office shall begin at the close of the meeting at which they are elected.
\section*{Section 4} Vacancies in offices may remain unfilled if there are no interested members so long as a minimum of four (4) officers are in office at any time. Positions held vacant may be filled by nomination and voting of a quorum of active members
\section*{Section 5} Officers shall have completed all courses satisfactorily in previous terms. This requirement does not apply to first-term freshmen or first-term transfer students.
\section*{Section 6} Officers shall be registered students.
\section*{Section 7} Officers shall not be on disciplinary probation.
\section*{Section 8} Officers shall have a minimum cumulative GPA of 2.00 and not have been on probation for the most recently completed term prior to the term of election, unless they obtain approval from a group faculty advisor.
\section*{Section 9} A graduate student must pay student fees and meet the same requirements as an undergraduate student with the exception that full time status shall be a minimum of 6 hours with a minimum cumulative GPA of 2.00.
\section*{Section 10} The President will be solely responsible for the successful and timely completion of mission tasks and group goals. In addition, the president will be solely in charge of appointing group leader positions and delegating member tasks throughout the group. The overall success of ALL group activities, events, and outreaches is the Presidents responsibility. The President will additionally be responsible for the delegation of tasks to other officers, group leaders, and group members.
\section*{Section 11} The Vice-President shall be responsible for assisting the president in his or her duties during their term of service, ensuring that all tasks get completed in a timely, organized, and efficient manner. The Vice-President will have the power to delegate tasks to other members and officers of the OSU-ARC organization as long as they have presidential approval for the tasks being executed.
\section*{Section 12} The Station Manager will be responsible for maintaining club equipment, and ensuring all equipment conforms to all relevant regulations. They are also to inspect station equipment for safety issues on a regular basis. 
\section*{Section 13} The Treasurer shall keep track of all funds and transactions that the OSU-ARC organization is involved in. The treasurer WILL NOT have complete control over the allocation of OSU-ARC funds; they will simply keep track of funds and provide regular (monthly) financial reports regarding the economic status of the OSU-ARC organization. All miscellaneous spending transactions must first be approved by one of the following:
The OSU-ARC organizations head faculty advisor
The OSU-ARC president
The OSU-ARC vice-president, when acting under direct order of the faculty advisor or the president.
A motion approved by a simple majority of a quorum is required for any spending that exceeds \$100 in a thirty day period.
\section*{Section 14} The Secretary shall be responsible for taking notes on each OSU-ARC group meeting, monitoring the OSU-ARC website, and posting updates as to all current OSU-ARC events and projects on the OSU-ARC website, as well as the OSU-ARC website. In addition the secretary will be responsible for weekly group emails, and bi-weekly scheduling of group meetings. This includes meeting with group advisors, group leaders, and other officers when necessary so that they can include the agenda of the next weekly meeting in the group weekly meeting reminder email.



\part{Meetings}

\section*{Section 1} There shall be regular meetings, the schedule of which will change on a term-by-term basis by the group. Meetings will not be held during finals week. Special meetings will be announced at least THREE days in advance.
\section*{Section 2} The first Tuesday meeting in April shall be known as the annual meeting and shall be for the purpose of electing officers, receiving reports of officers and committees, and for any other business that may arise.
\section*{Section 3 } Special meetings may be called by the President or the Executive Committee and shall be called upon the written request of the association, and will provide at least THREE days notice. The purpose of the meeting shall be stated in the notice and three days' notice shall be given except in cases of emergency.
\section*{Section 4} The by-laws shall be determined by a majority vote. Fifty-one percent (51\%) of the members of the association shall constitute a quorum.

\part{Relationships with Other Organizations}

OSU-ARC will not be controlled or governed by any other local, state or national organization. The OSU-ARC organization will work hand in hand with many research groups, but will not be under the control of any of these groups or organizations.

\part{Activities}

Group Meetings

The association shall hold regular meetings (discussed in Article V, Section 1). Meetings may include the following:

Evaluation of the current mission status in accordance with the group goals and mission timeline.
Officer \& Group Leader presentation regarding the status of individual projects. These presentations will include the current status of the group as well as obstacles encountered, current obstacles, current plans, and summary of how the project fits in conjunction with project time-lines.
Guest speakers on project related topics.
Guest speakers on additional scientific topics.
Future projects \& how to implement them into in conjunction with the OSU-ARC group goals established and in place.


\part{Committees}

\section*{Section 1} The Executive Committee shall include the officers of the association. They shall supervise affairs of the association between its business meetings, make recommendations to the association and perform other duties as specified in the constitution and bylaws. The Executive Committee shall be subject to the orders of the association and none of its actions shall conflict with actions taken by the association.
\section*{Section 2} Other committees, standing or special, shall be appointed by the President as the association or the Executive Committee deems necessary to carry on the work of the association.


\part{Advisor}

An advisor shall be selected for the club, they will be under the sponsoring unit and accepted by the Executive Committee. Additional advisors may be selected from OSU faculty. Responsibilities shall be those assigned by Oregon State University's Student Conduct Regulations. In addition industry and community member advisors may also be selected for the purpose of advising and assisting the club, there will be no compensation for any advisor provided by the club.

\part{Parliamentary Authority}

FCC guidelines will be followed.

\part{Amendments}

This constitution may be amended at any regular meeting of the association by two-thirds vote, provided that the amendment has been submitted in writing at a regular meeting.

\part{By-Laws}

By-laws may be determined as described in Article VI, Section 4. The purpose of by-laws are to further refine the rules and operation procedures for the club. By-laws expire seven days before the start of the fall term. By-laws may be renewed, re-made from scratch or left to expire.

\part{Over Rules \& Authoritative Overrides}

All rules, guidelines, and regulations described by the constitution and by-laws are subject to being over ridden by EITHER

A faculty advisor express written approval override submitted directly to the President and discussed between the officers and faculty advisors.
OR
A two-thirds member vote by anonymous ballot.
OR
In any case where the constitution or by-laws conflict with any applicable law or OSU regulation the law or regulation shall take precedence.

If the matter being referenced is an officer status, that officer shall not attend the meeting between faculty advisors and officers.

\end{document}