\documentclass[10pt,letterpaper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb} 
\usepackage[left=0.25in, right=0.25in, top=0.25in, bottom=0.25in]{geometry}
\title{W7OSU transition information}
\begin{document} 
\maketitle
This document is intended to help new officers hit the ground running. 

The club has two repeaters the 147.16MHz on Vineyard Mtn, and the 443.05MHz on Dearborn hall. Key's to access both sites are on the club lanyard. The '7.16 is coordinated through the Oregon Region Relay Council http://orrc.org. Dues are currently \$15 per year, and are due in January. The 443.050 repeater is not currently coordinated, if there is interference with a coordinated machine then it will need to be turned off. An option would be to re-crystal the repeater a GE Master II to a different frequency, this would be very expensive. Before accessing the Dearborn penthouse someone needs to contact Tom Williams, the room has an alarm system and if he doesn't know then Campus Security may be called. Contact information is in a following section.

The club has money in two accounts. One is the MU account, account number MUNZ79 someone need to be signed on as the ``owner'' of the account, they have full control over the account, and if they over-draw the account the balance is charged to their student account. This shouldn't be an issue as any money withdrawn is checked against the balance before being withdrawn. The other is an US bank account, the club adviser is a signer for the account.

Every year the club needs to renew it's position with the university. This is done through the Student Leadership and Involvement site (search OSU for SLI url's change too often) It is pretty simple, most of the information should already be in the system. Enter the names for the new officers, double check the risk assessment and get the adviser and department head to ``sign off'' which is done by them clicking a link sent to their onid's.

The access to the club's room is done with a door code which can be given to any members and after-hours access through the KBVR door with a code also given out to members. At least one officer should talk to the student media personnel about about getting a key to the room in case the door has issues. Once student media moves out of Snell someone will need to find out where to get keys.

Contacts that may prove useful are:
\begin{itemize}
	\item John Stanley N8GFO stanley@peak.org - BCARES a good guy for repeater stuff.
	\item Chris Novara AB7BS chris@redcrosscommunications.org - works for Silke Communications has all sorts of cool toys for repeater testing
	\item David Hackleman W7QH david.hackleman@oregonstate.edu OSU professor and friend of the club. Has a great collection of old radios
	\item Don Reid W7DMR don@db-reid.com EC for Benton County ARES
	\item Tom Williams KA7UPD thomas.e.williams@oregonstate.edu Campus technology, and guy who controls the dearborn penthouse space
	\item Todd Shechter K7FAI shechter@engr.orst.edu COE Fallcitities guy, and head of Corvallis Mountain Rescue Unit
	\item Jon Kenneke K7PGB jkenneke@opb.org OPB site Engineer
	\item Sara Roberston sara.robertson@oregonstate.edu Campus planning
	\item Jean Deffett jean.duffett@oregonstate.edu Campus planning
	\item Rosemarie DeBono rosemarie.debono@oregonstate.edu Campus planning
\end{itemize}

\end{document}